%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.85]{geometry}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\textcolor{color1}{Thomas}}
\familyname{\textcolor{color1}{Chauvet}}

\address{Geneva, Switzerland}{}{}
\homepage{thomas.chauvet@icloud.com}
\social[linkedin]{www.linkedin.com/in/thomaschauvet/}{}
\social[github]{www.github.com/thomas-chauvet/}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\vspace{-1.5cm}

\begin{center}
    \Large{\textbf{\textcolor{color1}{Artificial Intelligence Engineer}}} - 5 years of experience
\end{center}

\textcolor{color2}{Data enthusiast, my aim is to build data products relying on artificial intelligence to help solving real life issues such as impact on justice and social change.}

\vspace{0.4cm}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{May 2019 \\--\\ Present}{Artificial Intelligence Engineer}{\textsc{International Committee of the Red Cross (ICRC)}}{Geneva, Switzerland}{}{
\textit{Artificial Intelligence Engineer at ILEM Group (consulting company) in contract with ICRC.}
\textit{Note that most of the project is confidential. Two engineers, including myself, in the tech-team.}
\begin{itemize}
    \item \textbf{Search engine on multiple distributed and segregated databases} with textual, image and date fields. Focus on search (date, text and image), data pipelines, streaming engine, back-end and industrialization of the product.
    \item Product developed in \textit{Python}. APIs developed with \textit{FastAPI}. Use of \textit{ElasticSearch} search algorithms. Data pipelines based on \textit{Kafka} topics with \textit{Faust} streaming engine. Use of \textit{Kafka-connect} to pull and push data from/to \textit{Kafka} and \textit{Kafka-rest} in order to interact with topics with a \textit{REST} API.
    \item Deploy \textit{Docker} containers (one per module) via \textit{Ansible}. Use of TFS to build \textbf{continuous integration pipelines} (unit testing, code analysis, report to \textit{SonarQube},  build \textit{Docker} images) and \textbf{continuous release pipelines} (deploy different versions on different IT environments thanks to \textit{Ansible}).
\end{itemize}
Technology stack: Python (\textit{Faust, FastAPI}), Elasticsearch, Kafka, Docker, Ansible.
}

\vspace{0.8cm}


\cventry{Aug. 2017 \\--\\ March 2019}{Data Scientist / Data Engineer}{\textsc{Bleckwen} Fintech start-up}{Paris, France}{}{
\begin{itemize}
    \item R\&D project for 6 months on \textbf{temporal graph and text mining} to fight fraud. Use of graph mining to extract patterns and find anomalies in transactions network.\break
    Use of \textbf{Natural Language Processing (NLP)} to summarize text and find relevant patterns.\break
    Project built with \textit{Python} (\textit{Scikit-Learn}, \textit{Keras}, \textit{Pandas} for machine learning and exploration) and \textit{R}/\textit{Shiny} to communicate results with stakeholders with a web application.\break
    Presentation of \textit{LSTM} (neural network method) for NLP application based on a Kaggle dataset (slides on my \textit{GitHub}).
    \item Development of an anti-fraud product for banks. \textbf{Streaming machine learning} engine to score transactions (transfers, cards payments, credits) with high latency constraints (100ms to give a score with a throughput of 10'000 messages/second).\break
    Main responsibility on engine module. Read data from \textit{Kafka} and processed them with \textit{Flink}.\break
    Data pipeline in 3 steps: integrating data in the data model, feature engineering and transactions scoring with a machine learning model (\textit{Xgboost}). Add (hot) machine learning model deployment and machine learning interpretability in the streaming engine. Collaboration on the data storage and KPIs creation to monitor and store results from the engine.\break
    Product built in \textit{Scala} and deployed with \textit{Docker} (\textit{docker-compose}).
\end{itemize}
Technology stack: Python (\textit{Pandas, scikit-learn, Keras}), Kafka, Flink, Docker.
}

\cventry{Feb. 2015\\--\\Jul. 2017}{Data Scientist}{\textsc{Deepki} Energy Efficiency start-up}{Paris, France}{}{
\begin{itemize}
    \item Data collection, cleaning and consolidation from different sources (invoices, telemetry, patrimonial data, activity).
    Use of Machine learning to understand buildings consumption thanks to unsupervised learning (clustering). Use of supervised learning to \textbf{predict consumption}, to detect anomalies, and to simulate renovation impact. Use of load curves (instant power every 10 minutes) to \textbf{detect anomalies} at a day level thanks to an hybrid method based on \textit{Isolation Forest} and \textit{One-class SVM}.
    \item First employee to work on the product creation. Software as a Service (SaaS) product built in \textit{Shiny} as a Web application to visualize, understand, find patterns in energy data and manage recommendations and alerts.
    \item Supervision of two engineering school student projects.
\end{itemize}
Technology stack: Python (\textit{scikit-learn, Pandas, Flask}), R (\textit{tidyverse: dplyr, tidyr, ggplot2, Shiny}).
}

\vspace{0.7cm}

%\cventry{Jul. -- Sept. 2014}{Data Scientist Intern}{\textsc{French National %Public Health Agency - formerly InVS} Montpellier, France}{}{}{The aim of %the internship was the early detection of aberration like epidemic %outbreak, bacteriological attack, etc. on time series data.
%\begin{itemize}
%\item  Analyze and implement methods to detect unusual events based on %CUSUM (CUmulative SUM) and its variation on real time series data in %\textit{R}. Selection of the most relevant methods and combination to %increase the reliability of the warning system, 
%\item Development of an interactive tool in \textit{Shiny} to visualize %epidemiological time series and manage alerts (detection of epidemic %peaks). Users were epidemiologists.
%\end{itemize}
%}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2012 -- 2015}{INSA}{Toulouse, France}{French Graduate Engineering School}{}{Engineering degree (M.Sc.) in computational and mathematical engineering, specialization in statistical methods and models option Data Science.}  % Arguments not required can be left empty

\cventry{2009 -- 2012}{INSA}{Lyon, France}{}{}{Intensive undergraduate-level preparation in advanced Science (Mathematics, Physics, Mechanics, Chemistry).}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Languages}{Python, R, Scala}
\cvitem{Libraries}{Scikit-Learn (machine learning), Keras (deep learning), Pandas (data wrangling/manipulation), Shiny (web application in R), tidyverse (colection of R packages for data science), FastAPI (asynchronous Python API - REST - GraphQL)}
\cvitem{Frameworks}{Kafka ecosystem (distributed stream-processing software platform), Faust (python streaming engine), Elasticsearch}
\cvitem{Tools}{Git, Docker, Ansible}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}
\cvitem{}{
Native \textbf{French} speaker.
Fluent in \textbf{English} (TOEIC: 900).
Basic \textbf{Spanish}.
}

\end{document}